---
title: " Research on the relationship between forearm length and height (0280)"
author: "SS1234 (.)"
date: "September 26, 2020 (.)"
output: html_document
---


## I. Introduction 

- the title of assignment #1 is "Research on the relationship between forearm 
length and height".

- I randomly select the data from 10 adults in the class in the file provided by
by September 17.
```{r}
dataz<-read.csv("a20a1data.csv")
set.seed(0280)
data0280<-sample_n(dataz,10,replace=FALSE)
data0280
```

- The explanatory variable is the height and the response variable is the forearm length since I believe higher people tend to have longer forearm length and want to explore the relationship between them.

## II. Exploratory Data Analysis

```{r}
library(tidyverse)

ggplot(data0280,aes(x=height, y=forearm))+
  geom_point()+
  labs(title="Scatterplot of forearm length / height (0280)",
       x="height", y = "forearm length")+
  theme_classic() +
  geom_smooth(method=lm,  linetype="solid",
             color="darkred", fill="blue")

ggplot(data=data0280, aes(forearm)) + 
  geom_histogram(binwidth = 1) +
  ggtitle("Distribution of forearm length")

ggplot(data0280, aes(x=forearm)) + 
  geom_boxplot() +
  ggtitle("boxplot of forearm length v.s height (0280)")

```
- my response variable non-normal as can be discovered from the histogram since 
the graph of histogram are right-skewed. 

```{r}
summary(data0280)
summarise(data0280,var=var(forearm))
```
- The median forearm length is 23.75 cm, the mean forearm length is 23.66 cm.
  The variance for the length of forearm is 58.28267.
  There are two unusual data point which are identifiable from the boxplot which 
  is the 9.2 cm and the 40.0 cm of the forearm length.



## III. Methods and Model

```{r}
RL<-lm(forearm~height, data=data0280)
RL
```
- the model of the regression line  can be seen as ŷ = -39.3510 + 0.3668x

- the regression parameters are not zero

- slope estimate: when height increases by 1 cm, the corresponding average change    in the forearm length is 0.3668 cm
  intercept estimate: the average length of forearm when the height is equal to
  0 cm. However, this does not have any practical meaning since the height of
  human being will not be 0 cm.
   


## IV. Discussions and Limitations
- Disability, ages, races, are all lurking variable for the forearm length.
  By identifying the scatterplot, it's not likely that the data are in a linear
  relationship because of the two unusual point and my fit line is not capable 
  of catching these points. When studying the how the forearm length are being 
  affected by height, we want to focus on healthy people who do not suffer from
  disability and genetic mutations. Thus by removing the outliers and               reconstructing the graph, I am getting a new fitted line below which is better.
  
```{r}
data2<-filter(data0280,id!="2")
data3<-filter(data0280,id!="319")
ggplot(data3,aes(x=height, y=forearm))+
  geom_point()+
  labs(title="Scatterplot of forearm length / height (0280)(2)",
       x="height", y = "forearm length")+
  theme_classic() +
  geom_smooth(method=lm,  linetype="solid",
             color="darkred", fill="blue")
```
  
- Another pair of variables that can be used to explore a simple linear 
  regression model is age and forearm length. The response variable is forearm
  length and the explanatory variable is the age.
  
  
  
  
  
  
  
  
  
  
  
  
